Analysis plan

### 2023-02-08 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Adding more detail to the study design, and last few sections, added table names and numbers throughout document

# Analysis Plan

@@

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month. [We
currently have Nov 2022 and Dec 2022 updates; I will try to track down
past months. Ideally, we will merge in each monthly check-in file with
the preceding month's roster file.]

#### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.

@@

#### Table 2. GSA Roster Variables.

@@

For all analysis, we will used a defined cohort of staff to examine work
status over period of time. A cohort of staff employed in the month of
March 2022 will be followed over six months. Teams will be defined by
the supervisors of groups of staff in the beginning of March 2022. Any
analysis will conduct may be reproduced on a separate cohort or may be
combined with multiple cohorts depending on the data availability.

@@

The analysis will be done for staff and teams separately

```{r, echo=FALSE}
tbl <- 
  tibble::tibble(
    # level = rep("Level of analysis",2),
                      Group = c("Staff", "Team"),
                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
                      # Sequence = c("Daily person work status", "Daily team work status")
                       )
```

@@

Missing data from daily check in will be treated as follows:

@@

Missing data from the roster will be treated as follows:

@@

The figure below shows an example of the this. The total within sum of
squares decreases with the number of clusters. In this example, three
clusters appears to be the point where the returns to more cluster
diminishes.

@@

@@

@@

@@

@@

>>>>

```{r}
table_n <- 0
```

@@

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month. 
<!-- [We currently have Nov 2022 and Dec 2022 updates; I will try to track down -->
<!-- past months. Ideally, we will merge in each monthly check-in file with -->
<!-- the preceding month's roster file.] -->

```{r}
table_n <- table_n + 1
```

#### Table `r table_n`. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.

@@

```{r}
table_n <- table_n + 1
```

#### Table `r table_n`. GSA Roster Variables.

@@

For all analysis, we will used a defined cohort of staff to examine work
status over period of time. A cohort of staff employed in the month of
March 2022 will be followed over six months. Teams will be defined by
the supervisors of groups of staff in the beginning of March 2022. Any
analysis we conduct may be reproduced on a separate cohort or may be
combined with multiple cohorts depending on the data availability.

@@

The analysis will be done for staff and teams separately and aggregated independently. The table below defines how we plan to aggregate for staff and teams.

```{r}
table_n <- table_n + 1
```

#### Table `r table_n`. Level of analysis and aggregation

```{r, echo=FALSE}
tbl <- 
  tibble::tibble(
    # level = rep("Level of analysis",2),
                      Group = c("Staff", "Team"),
                      Aggregation = c("Person level aggregation of work status", "Team level aggregation of work status"),
                      # Sequence = c("Daily person work status", "Daily team work status")
                       )
```

@@

Missing data from daily check in will be treated as defined in the table below.

```{r}
table_n <- table_n + 1
```

#### Table `r table_n`. Treatment of missing data from daily check in

@@

Missing data from the roster will be treated as show in the table below.

```{r}
table_n <- table_n + 1
```

#### Table `r table_n`. Treatment of missing data from roster

@@

The figure below shows an example of the this. The total within sum of
squares decreases with the number of clusters. In this example, three
clusters appears to be the point where the returns to more cluster
diminishes. We will also construct silhouette charts to confirm the number of clusters.

@@

The staff statistics will be calculated for the following groups:

1.    Whole cohort of staff
2.    By rule-based categories of work pattern
3.    By cluster defined categories of work pattern

The team statistics will be calculated for the following groups:

1.    Whole cohort of teams
2.    By rule-based categories of work pattern
3.    By cluster defined categories of work pattern

Another set of statistics will be designed to understand the relationship between staff work patterns and their supervisor. We will calculate  the proportion of the staff that fall into the same rule-based and clusters as their supervisors overall as well as by those categories.

These statistics will be presented in tables. Visualizations will be created for a subset to help communicated results. Charts of the work pattern data will be created to confirm and characterize the groupings. In addition, charts showing difference by stated telework position category.

@@

We plan no confirmatory analyses.

@@

We plan no exploratory analyses. Though, all this work may be considered exploratory.

@@

We will not be making any inference.

@@

This is non causal research. The work will not demonstrate if changes or attributes caused differences, only if there are relationships. K-means clustering can be sensetive to the random locations of the first points selected to calculate differences and define clusters.
